\documentclass[11pt,a4paper]{article}

\usepackage[headheight=100pt]{geometry}
\usepackage{fancyhdr}   % custom headers
\usepackage{lipsum}     % insert dummy 'Lorem ipsum' text
\usepackage{amsmath}    % measurement fractions
\usepackage{multicol}   % multi column for ingredients
\usepackage{hyperref}   % links
\usepackage{siunitx}    % degrees Celsius and measures
\usepackage{times}      % alternate font
\usepackage{textcomp}   % temperature

\pagestyle{fancy}
\fancyhf{}  % clear header and footer
\fancyhead[L]{\fontsize{14}{10} \selectfont Carrot-Celery-Potato Soup}

\begin{document}

\subsection*{Ingredients}

\begin{multicols}{2}

\begin{itemize}
  \item $ 1 $ medium onion, minced
  \item $ 2 $ medium potatoes, cooked
  \item $ 2 $ medium carrots, diced
  \item $ 2 $ stalks celery, diced
  \item $ 1 $ teaspoon olive or vegetable oil
  \item water or vegetable stock as needed
\end{itemize}

\columnbreak

\begin{itemize}
  \item $ 5 $ cloves garlic
  \item $ 1 $ tablespoon grated ginger
  \item $ \frac{1}{2} $ teaspoon turmeric
  \item $ \frac{1}{2} $ teaspoon cayene pepper
  \item $ 1 $ teaspoon ground black pepper
  \item $ 3 $ or $ 4 $ sage leaves, minced
  \item $ \frac{1}{2} $ cup soy or cow milk
\end{multicols}

\medskip

\subsection*{Method}

\begin{enumerate}
  \item Heat the oil in a skillet. Add the onions and saute over medium heat, stirring occasionally, until they become translucent, for about 5 minutes.
  \item Add the ginger and garlic and stir for another minute.
  \item Add the carrots, celery, cayenne, turmeric and ground black pepper. Stir and saute another 2-3 minutes until the carrots begin to soften.
  \item Add enough water or stock to cover the vegetables, bring to a boil, turn down the heat, and simmer, covered, until the carrots are very tender, for about 8-10 minutes.
  \item Add the cooked potatoes (make sure they are tender) and stir in.
  \item Put all the vegetables and liquid into a blender and blend into a puree.
  \item Pour the vegetable puree back into the skillet over medium heat, add the milk, and let everything warm through.
  \item Add salt to taste, then the sage leaves.
\end{enumerate}

\end{document}
