\documentclass[11pt,a4paper]{article}

\usepackage[headheight=100pt]{geometry}
\usepackage{fancyhdr}   % custom headers
\usepackage{amsmath}    % measurement fractions
\usepackage{multicol}   % multi column for ingredients
\usepackage{hyperref}   % links
\usepackage{times}      % alternate font
\usepackage{textcomp}   % temperature

\pagestyle{fancy}
\fancyhf{}  % clear header and footer
\fancyhead[L]{\fontsize{14}{10} \selectfont Greek Style Baked Vegetables}

\begin{document}

\subsection*{Ingredients}

\begin{multicols}{2}

\begin{itemize}
   \item potato
   \item onion
   \item squash
   \item capsicum
   \item eggplant
   \item plus other vegetables ...
\end{itemize}

\columnbreak

\begin{itemize}
   \item garlic
   \item chilli
   \item tomatoes ($\frac{1}{2}$ to blend, $\frac{1}{2}$ to layer on top)
   \item tomato paste
   \item salt and pepper
\end{itemize}

\end{multicols}

\medskip

\subsection*{Method}

\begin{enumerate}
   \item Slicing your vegetables.  Heat olive oil in a large saucepan. Saute the potatoes, squash, onion and eggplant, until coloured.
   \item Place potatoes in a layer on the bottom of an oven proof pan.  Layer vegetables, mixing some of the onions and peppers throughout.  Top with tomatoes, parsley and season with salt and pepper.
   \item Blend part of the tomatoes, tomato paste, one small chilli and garlic with water. Pour over the top of the vegetables.  Drizzle some olive oil over the top and place in a preheated 200\textdegree C oven. After 30 minutes, remove the dish and baste vegetables with their juices.  Reduce the oven to 150\textdegree C and cook for another hour.  Check it every 20 minutes to make sure the liquid isn't too low.  If you need to, top with a little more water.  If the vegetables are browning too quickly, cover it with foil.
   \item Remove from oven when the vegetables are a little charred on top and soft.  Squeeze two fresh lemons over the vegetables. Let it stand for 10 - 15 minutes before serving.
\end{enumerate}

Source: \href{https://www.artfrommytable.com/baked-vegetable-medley-greek-style/}{Baked Vegetable Medley (Greek Style)}

\end{document}
