\documentclass[11pt,a4paper]{article}

\usepackage{fancyhdr} % custom headers
\usepackage[headheight=100pt]{geometry}
\usepackage{lipsum}   % insert dummy 'Lorem ipsum' text
\usepackage{amsmath}  % measurement fractions
\usepackage{multicol} % multicolumn for ingredients
\usepackage{hyperref} % links
\usepackage{times}    % alternate font

\pagestyle{fancy}
\fancyhf{}  % clear header and footer
\fancyhead[L]{\fontsize{14}{10} \selectfont Japanese Style Beef Curry}

\begin{document}

\subsection*{Ingredients}

\begin{multicols}{2}

\textbf{For beef marinade}

\begin{itemize}
  \item $ 500 $ cubed grams beef
  \item $ 4 $ tablespoons \href{https://en.wikipedia.org/wiki/Tamari}{Tamari}
  \item $ 1 $ tablespoons sake
  \item $ 1 $ tablespoons hot curry powder
  \item $ 2 $ teaspoons cornflour
  \item $ 1 $ teaspoon corn or olive oil
  \item $ 2 $ cloves crushed garlic
  \item $ 1 $ teaspoon grated ginger
\end{itemize}

\columnbreak

\textbf{For the sauce}

\begin{itemize}
  \item $ 2 $ teaspoons cornflour
  \item $ 175 $ ml beef stock
  \item $ 2 $ teaspoons \href{https://en.wikipedia.org/wiki/Tamari}{Tamari}
  \item $ 1 $ teaspoon sake
  \item $ 4 $ tablespoons whipping cream
\end{itemize}

\textbf{For the final cooking}

\begin{itemize}
  \item $ 3 $ tablespoons corn or olive oil
  \item $ 1 $ medium onion, thickly sliced
  \item $ 2 $ medium carrots, thickly sliced
  \item $ 3 $ medium potatoes, cubed (pre-cooked)
\end{itemize}

\end{multicols}

\medskip

\subsection*{Method}

\begin{enumerate}
  \item To marinate the meat, place into a bowl, add all marinade ingredients, and mix well.
        Cover and set refrigerate for 2 hours.
        
  \item To make the sauce, mix together sauce ingredients. Set aside.
  
  \item When ready to cook the curry, pour oil into a large pan and set over a medium heat.
        Add the onions and carrots. Stir and fry for about 4 minutes or until onions are 
        slightly translucent.
        
  \item Add the meat, together with its marinade and fry, continuing to stir, for a minute.
  
  \item Cover, reduce the heat to medium low, and cook for about 5 minutes, lifting the lid
        to stir the contents now and then.
        
  \item Take pan off the heat. Stir the sauce and add to the pan. Stir and put pan back on
        the medium-low heat.
        
  \item Add potatoes. Cook for a minute until potatoes hot.
  
  \item Serve. 
        I normally serve on baby spinach leaves. The heat from the curry will soften the spinach.
        
\end{enumerate}

\end{document}
