\documentclass[11pt,a4paper]{article}

\usepackage{fancyhdr} % custom headers
\usepackage{lipsum}   % insert dummy 'Lorem ipsum' text
\usepackage{amsmath}  % measurement fractions
\usepackage{multicol} % multicolumn for ingredients

\pagestyle{fancy}
\fancyhf{}  % clear header and footer
\fancyhead[L]{\fontsize{14}{10} \selectfont Moghlai Lamb with Spinach (Paalag Gosht)}

\begin{document}

\subsection*{Ingredients}

\begin{multicols}{2}

\begin{itemize}
  \item $ 500g $ Lamb, cubed
  \item $ 1 $ teaspoon garlic
  \item $ 1 \frac{1}{2} $ teaspoon ginger
  \item $ 1 $ teaspoon coriander
  \item $ 4 $ small shallots, sliced
  \item $ 3 $ tablespoons corn or peanut oil
\end{itemize}

\columnbreak

\begin{itemize}
  \item $ 1 $ teaspoon turmeric
  \item $ \frac{1}{2} $ teaspoon cayenne pepper
  \item $ \frac{1}{2} $ teaspoon salt
  \item $ 4 $ tablespoons natural yoghurt
  \item $ 200g $ spinach, roughly chopped
\end{itemize}

\end{multicols}

\medskip

\subsection*{Method}

\begin{enumerate}
  \item Put the meat into a bowl, add ginger, garlic and coriander; mix well and set aside for 30 minutes.
  \item Pour oil in wide pan. When hot sit in onions, and fry them until golden and crisp.
  \item Remove onions with slotted spoon and spread on kitchen paper, leaving as much oil behind as possible.
  \item Reduce heat to medium, put in the meat with marinade. Add turmeric, cayenne and salt, stir for a minute.
  \item Cover and cook for 10 minutes. Stir occasionally.
  \item Remove lid, add 1 tablespoon of yoghurt. Stir until the yoghurt is absorbed. Add each tablespoon of yoghurt in this way.
  \item Stir in the spinach.
  \item Add the fried onions.
  \item Continue to stir until the spinach has wilted.
  \item Cover pan and cook on very low heat for about 50 minutes or until the meat is tender. Lift lid occasionally to stir.
  \item If the liquid seems to have dried up completely, add a few tablespoons of water at a time and cover again. The spinach should cling to the meat.
  
\end{enumerate}

\end{document}
