\documentclass[11pt,a4paper]{article}

\usepackage{fancyhdr} % custom headers
\usepackage[headheight=100pt]{geometry}
\usepackage{lipsum}   % insert dummy 'Lorem ipsum' text
\usepackage{amsmath}  % measurement fractions
\usepackage{multicol} % multicolumn for ingredients

\pagestyle{fancy}
\fancyhf{}  % clear header and footer
\fancyhead[L]{\fontsize{14}{10} \selectfont Mon's Meatballs}

\begin{document}

\subsection*{Ingredients}

\begin{multicols}{2}

\subsubsection*{Sauce}

\begin{itemize}
  \item $1$ brown onion, finely chopped
  \item $2$ cloves garlic crushed
  \item $2$ tablespoons tomato paste
  \item $400g$ canned diced tomatoes
  \item $2$ cups beef stock
  \item $300g$ spaghetti (or 100g per person)
  \item $\frac{1}{2}$ cup fresh parmesan cheese to serve
  \item Basil leaves (optional)
\end{itemize}

\columnbreak

\subsubsection*{Meatballs}

\begin{itemize}
  \item $500g$ beef minced
  \item $1$ brown onion, grated
  \item $1$ carrot peeled, grated
  \item $\frac{1}{4}$ cup fresh parsley finely chopped
  \item $\frac{3}{4}$ cup fresh multigrain breadcrumbs
  \item $125g$ feta diced
  \item $1$ egg beaten
  \item plain four (for dusting meatballs)s
\end{itemize}

\end{multicols}

\medskip

\subsection*{Method}

\begin{enumerate}

  \item Make meatballs by combining mince, onion, carrot, parsley, breadcrumbs,
    feta, egg, salt {\&} pepper in a bowl, mixing well.

  \item Place four on a plate. Roll heaped tablespoonfuls of mixture into balls.
    Roll meatballs in four to coat.

  \item Heat oil in large non-stick frying pan. Cook meatballs in batches until
    browned (about 2 minutes). Transfer to plate.

  \item Wipe pan clean {\&} heat oil over med heat. Add onion {\&} garlic. Stir
    {\&} cook until onion soft.

  \item Add tomato paste {\&} cook stirring for 1 minute.

  \item Add tomatoes {\&} beef stock to pan. Bring to boil. Reduce heat to
    med-low {\&} simmer, about 15-20 mins.

  \item Add meatballs to sauce {\&} spoon over sauce to coat. Cook covered for
    about 15 minutes. Take lid off during last 5 minutes to thicken sauce.

  \item In the meantime, cook spaghetti.

  \item Arrange spaghetti in bowls {\&} spoon over meatballs {\&} sauce. Top
    with parmesan cheese {\&} basil.

\end{enumerate}

\end{document}
