\documentclass[11pt,a4paper]{article}

\usepackage[headheight=100pt]{geometry}
\usepackage{fancyhdr}   % custom headers
\usepackage{lipsum}     % insert dummy 'Lorem ipsum' text
\usepackage{amsmath}    % measurement fractions
\usepackage{multicol}   % multi column for ingredients
\usepackage[colorlinks = true, linkcolor = blue, urlcolor  = blue, citecolor = blue, anchorcolor = blue]{hyperref} % links
\usepackage{siunitx}    % degrees Celsius and measures
\usepackage{times}      % alternate font
\usepackage{textcomp}   % temperature

\pagestyle{fancy}
\fancyhf{}  % clear header and footer
\fancyhead[L]{\fontsize{14}{10} \selectfont Potato and Cauliflower Curry}

\begin{document}

\subsection*{Ingredients}

\begin{multicols}{2}

\begin{itemize}
  \item vegetable oil
  \item large onion or shallots
  \item ginger
  \item garlic
  \item $\frac {1} {2}$ teaspoon turmeric
  \item 1 teaspoon ground cumin
  \item 1 teaspoon curry powder
\end{itemize}

\columnbreak

\begin{itemize}
  \item 225 \si{\gram} chopped tomatoes
  \item 1 cauliflower, cut into florets
  \item 2 potatoes, cut into chunks
  \item 1 small green chilli, cut length ways
  \item squeeze of lemon juice
  \item fresh coriander, to serve
  \item natural yogurt, to serve
\end{itemize}

\end{multicols}

\medskip

\subsection*{Method}

\begin{enumerate}
  \item Heat the oil in a saucepan. Cook the onion for 10 mins until soft, then add the ginger, garlic, turmeric, cumin and curry powder.
  \item Cook for a minute more.
  \item Stir in the tomatoes.
  \item Add the cauliflower, potatoes and split chilli, seasoning to taste.
  \item Cover with a lid and gently cook for a good 30 mins, stirring occasionally, until the vegetables are tender.
  \item Add a drop of water if you need to, but it is meant to be a dry curry.
  \item When the vegetables are cooked, remove the chilli, if you like, stir in a squeeze of lemon juice and scatter with coriander.
  \item Serve with a dollop of yogurt.
\end{enumerate}

\href{https://www.bbcgoodfood.com/recipes/cauliflower-potato-curry}{BBC Good Food}

\end{document}
