\documentclass[11pt,a4paper]{article}

\usepackage{fancyhdr} % custom headers
\usepackage[headheight=100pt]{geometry}
\usepackage{lipsum}   % insert dummy 'Lorem ipsum' text
\usepackage{amsmath}  % measurement fractions
\usepackage{multicol} % multicolumn for ingredients
\usepackage{hyperref} % links
\usepackage{siunitx}  % Centigrade
\usepackage{textcomp} % Centigrade
\usepackage{times}    % alternate font

\pagestyle{fancy}
\fancyhf{}  % clear header and footer
\fancyhead[L]{\fontsize{14}{10} \selectfont Vegetable Lasagne}

\begin{document}

\subsection*{Ingredients}

\begin{multicols}{3}

\textbf{Vegetables}

\begin{itemize}
  \item $ 3 $ large carrots
  \item $ 1 $ red capsicum
  \item $ 1 $ pumpkin
  \item $ 1 $ bunch spinach
\end{itemize}

\columnbreak

\textbf{Sauce}

\begin{itemize}
\item $ 1 $ tin diced tomatoes
\item $ \frac {1} {4} $ cup basil
\item $ 2 $ cloves garlic, crushed
\item $ \frac {1} {4} $ teaspoon chilli flakes
\end{itemize}

\columnbreak

\textbf{Lasagne}

\begin{itemize}
\item $ 2 $ cups cottage cheese
\item $ 9 $ wholemeal lasagne sheets
\item $ 2 $ cups cheese
\end{itemize}

\end{multicols}

\medskip

\subsection*{Method}

\begin{enumerate}
  \item Preheat oven to 220\textdegree C
  \item Prepare vegetables: In a large pan over medium heat, warm the olive oil. Once shimmering, add carrots, capsicum, pumpkin, and salt. Cook, stirring every couple of minutes, until vegetables are golden on edges, about 8 to 12 minutes.
  \item Add a few large handfuls of spinach. Cook, stirring frequently, until the spinach has wilted. Repeat with remaining spinach and cook until all of the spinach has wilted, about 3 minutes. Remove pan from heat and set aside.
  \item Prepare tomato sauce: Drain tomatoes. Transfer to food processor. Add the basil, olive oil, garlic, salt, and chilli flakes.
  \item Pulse mixture until tomatoes have broken down to an easily spreadable consistency. Pour the mixture into a bowl for later (about 2 cups). Clean food processor.
  \item Blend half cottage cheese (1 cup) until smooth. Transfer to large mixing bowl.
  \item Transfer cooked vegetables and spinach mixture to food processor. Pulse until they are more finely chopped (but not puréed!). Transfer the mixture to the bowl of whipped cottage cheese. Top with the remaining cottage cheese, then add $ \frac {1} {2} $ teaspoon salt (to taste) and lots of freshly ground black pepper. Stir to combine.
  \item Lasagne Assembly: Spread $ \frac {1} {2} $ cup tomato sauce evenly over the bottom of baking dish. Layer 3 lasagne noodles on top (snap off their ends to fit if necessary). Spread half of the cottage cheese mixture evenly over the noodles. Top with $ \frac {1} {3} $ cup tomato sauce, then sprinkle $\frac {1} {2} $ cup shredded cheese on top. Repeat $2$ more.
  \item Cover lasagne with aluminium foil, but don't let the foil touch the cheese). Bake, covered, for 18 minutes, then remove the cover and continue cooking for about 10 more minutes, until top is turning spotty brown.
  \item Remove from oven and let lasagne cool for 15 to 20 minutes, so it has time to set and cool down to a reasonable temperature. Sprinkle additional basil over the top, then slice and serve.
\end{enumerate}

\end{document}
