\documentclass[11pt,a4paper]{article}

\usepackage[headheight=100pt]{geometry}
\usepackage{fancyhdr}   % custom headers
\usepackage{lipsum}     % insert dummy 'Lorem ipsum' text
\usepackage{amsmath}    % measurement fractions
\usepackage{multicol}   % multi column for ingredients
\usepackage[colorlinks = true, linkcolor = blue, urlcolor  = blue, citecolor = blue, anchorcolor = blue]{hyperref}   % links
\usepackage{siunitx}    % degrees Celsius and measures
\usepackage{times}      % alternate font
\usepackage{textcomp}   % temperature

\pagestyle{fancy}
\fancyhf{}  % clear header and footer
\fancyhead[L]{\fontsize{14}{10} \selectfont Vegetarian Moussaka}

\begin{document}

\subsection*{Ingredients}

\begin{multicols}{2}

\begin{itemize}
  \item 2 medium eggplants, 1 cm slices
  \item 1 medium onion
  \item 250 \si{\gram} swiss brown mushrooms
  \item 1 cup green lentils
  \item 3 cloves garlic, minced
  \item 1 tin diced tomatoes
\end{itemize}

\columnbreak{}

\begin{itemize}
  \item 2 cups water
  \item 1 teaspoon oregano
  \item ground black pepper
  \item 1 tablespoon butter
  \item 2 tablespoon plain flour
  \item 2 cups milk
  \item $\frac{3}{4}$ cup grated Parmesan
\end{itemize}

\end{multicols}

\medskip

\subsection*{Method}

\begin{enumerate}
  \item Heat oven to $200\si{\celsius}$. In a single layer, lay eggplant rounds out on paper towel-lined baking sheets. Sprinkle salt on both sides of eggplant. Let sit 10 minutes, then pat dry with paper towels. Brush eggplants with 2 tablespoons oil and place on baking sheets in a single layer. Bake until tender, 12 minutes.
  \item In a large pot over medium heat, heat remaining 2 tablespoons oil. Add onion and mushrooms and cook until tender, 5 minutes. Add garlic and cook until fragrant, 1 minute more. Add lentils, tomatoes, and water. Season with oregano, salt, and pepper. Simmer until lentils are tender, 30 minutes. Add more water as necessary if sauce looks too thick.
  \item In a medium pot over medium heat, melt butter. Whisk in flour and cook 1 minute. Slowly pour in milk, whisking until no lumps remain. Cook until thickened, about 5 minutes, then add in Parmesan and stir until melted.
  \item Place yolks in a small bowl and lightly beat. Add about 2 tablespoons of bechamel and whisk to combine, then pour mixture back into bechamel and whisk until combined. Season with salt and pepper. Let simmer until thickened, about 5 minutes more.
  \item In a large baking dish, place a single layer of eggplants. Add half of the lentil mixture, then repeat with more eggplant and the rest of the lentils. Top with a final layer of eggplants. Spoon bechamel over eggplant and top with remaining $\frac{1}{4}$ cup of Parmesan. Bake until top is golden and heated through, 30 minutes.
\end{enumerate}

\href{https://www.delish.com/cooking/recipe-ideas/a30876085/vegetarian-moussaka-recipe/}{Vegetarian Moussaka by Makinze Gore}

\end{document}
